Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators

### 2019-02-12 Paper/paper.tex
add noncoplanar disc

% !TEX spellcheck = en-US
\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress,nobibnotes]{revtex4}%
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{epstopdf}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{fancybox}
\usepackage{amsfonts}
\usepackage{amssymb}%
\usepackage[toc,page]{appendix}
%\usepackage[backend=bibtex,natbib=true,sorting=none]{biblatex}
\setcounter{MaxMatrixCols}{30}

@@

\begin{equation}
\label{MKMH}
\hat{H}^0 = \hat{\mathcal{H}}_t + \hat{\mathcal{H}}_{\text{SOI}} + \hat{\mathcal{H}}_{\text{int}}
\end{equation}
Where:
\begin{align}
&\hat{\mathcal{H}}_t = - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} - \sum_{\langle \langle i,j \rangle \rangle, \sigma} t_2\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
&\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \\
&\hat{\mathcal{H}}_{\text{int}} = \text{U}_{00}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \sigma \sigma'} \text{U}_{ij}\hat{n}_{i\sigma}\hat{n}_{j\sigma'}
\end{align}

Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $\text{U}_{00}$ and $\text{U}_{ij}$ are the on-site and NN Coulomb interactions. $t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping. $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). $\sigma^{z}$ is the third Pauli matrix. 
In practice the NN Coulomb interaction can be effectively approximated by a reduced on-site interaction $\text{U} = \text{U}_{00} - \bar{\text{U}}$ where $\bar{\text{U}}$ is an average of the NN Coulomb interacion \cite{Schuler2013}, we therefore can take:
\begin{equation}
\hat{\mathcal{H}}_{\text{int}} \approx \text{U}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation}
With $\text{U} = \text{U}_{00} - \bar{\text{U}}$.

@@

%\begin{thebibliography}
\bibliography{../MT}
%\end{thebibliography}

>>>>

% !TEX spellcheck = en-US
\documentclass[aps,prl,twocolumn,amsmath,amssymb,superscriptaddress,nobibnotes]{revtex4-1}%
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{epstopdf}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{fancybox}
\usepackage{amsfonts}
\usepackage{amssymb}%
\usepackage[toc,page]{appendix}
%\usepackage[backend=bibtex,natbib=true,sorting=none]{biblatex}
\setcounter{MaxMatrixCols}{30}

@@

\begin{equation}
\label{MKMH}
\hat{H}^0 = \hat{\mathcal{H}}_t + \hat{\mathcal{H}}_{\text{SOI}} + \hat{\mathcal{H}}_{\text{int}}
\end{equation}
Where:
\begin{align}
&\hat{\mathcal{H}}_t = - \sum_{\langle i,j \rangle, \sigma} t_1\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} - \sum_{\langle \langle i,j \rangle \rangle, \sigma} t_2\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \label{Ht} \\
&\hat{\mathcal{H}}_{\text{SOI}} = \sum_{\langle \langle i,j \rangle \rangle, \sigma} i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma}\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} \label{Hsoi} \\
&\hat{\mathcal{H}}_{\text{int}} = \text{U}_{00}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow} + \frac{1}{2}\sum_{\langle i,j \rangle, \sigma \sigma'} \text{U}_{ij}\hat{n}_{i\sigma}\hat{n}_{j\sigma'} \label{Hint}
\end{align}

Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$, $\text{U}_{00}$ and $\text{U}_{ij}$ are the on-site and NN Coulomb interactions. $t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping. $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). $\sigma^{z}$ is the third Pauli matrix. Notice that Rashba SOI interactions are not included in \ref{Hsoi}, the reason is that such terms are not allowed by symmetry in the honeycomb lattice, however Rashba interactions should be considered in lower symmetry lattices such a non-coplanar honeycomb lattice \cite{Liu2011}.
In practice the NN Coulomb interaction can be effectively approximated by a reduced on-site interaction $\text{U} = \text{U}_{00} - \bar{\text{U}}$ where $\bar{\text{U}}$ is an average of the NN Coulomb interacion \cite{Schuler2013}, we therefore can take:
\begin{equation}
\hat{\mathcal{H}}_{\text{int}} \approx \text{U}\sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation}
With $\text{U} = \text{U}_{00} - \bar{\text{U}}$.

@@

%\begin{thebibliography}
\bibliographystyle{apsrev4-1}
\bibliography{../MT}
%\end{thebibliography}
